Sample-efficient Reinforcement Learning with Latent Representations

### 2024-01-29 paper/main.tex
aligned main eq

\begin{align}
\text{Encoder: } &z_{t} = e_{\theta} (s_{t}) \label{eq:encoder} \\
\text{Dynamics: } &\hat{z}_{t+1} = d_{\phi} (z_{t}, a_{t}) \label{eq:transition} \\
\text{Value: } &q_{t} = Q_{\psi} (z_{t}, a_{t}) \label{eq:value} \\
\text{Policy: } &a_{t} \sim \pi_{\eta} (z_{t}) , \label{eq:policy}
\end{align}
Note that unlike TCRL \citep{zhaoSimplifiedTemporalConsistency2023}, our transition model does
not predict the reward.

>>>>

\begin{align}
&\text{Encoder: } & z_{t} &= e_{\theta} (s_{t}) \label{eq:encoder} \\
&\text{Dynamics: } & \hat{z}_{t+1} &= d_{\phi} (z_{t}, a_{t}) \label{eq:transition} \\
&\text{Value: } & q_{t} &= Q_{\psi} (z_{t}, a_{t}) \label{eq:value} \\
&\text{Policy: } & a_{t} &\sim \pi_{\eta} (z_{t}) , \label{eq:policy}
\end{align}
Note that unlike TCRL \citep{zhaoSimplifiedTemporalConsistency2023}, our transition model does
not predict the reward.
